---
title: "Hsp90 stress and the Candida albicans genome"
output:
 #tufte::tufte_html: default
  tufte::tufte_handout: default
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
rm(list=ls())
library(ggplot2)
library(dplyr)
library(tidyr)
library(RColorBrewer)
library(grid)
library(MASS)
library(tufte)
library(reshape)
library(nnet)
source("~/Dropbox/! Diezmann Lab/R/FormatGGplot.R")
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.height=4, dev.args = list(bg = 'transparent'),
                      echo=FALSE, warning=FALSE, message=FALSE)
```


* * * 

##Summary of results

1. Increasing concentrations of the Hsp90 inhibitors Geldanamycin (GdA) and Radicicol (RAD) result in increased LoH rates
2. Perturbing Hsp90 levels by high temperature or Hsp90 inhibtor treatment results in increased LoH rates across the genome
3. 


* * * 

#Hsp90 inhibitor dose response

`r margin_note("- plotted are LoH rates with 95\\% confidence intervals")`
`r margin_note("- Strain used MYO1/MYO1::URA3, marking chromosome 5L ")`
`r margin_note("- subsequent experiments were conducted with 3 µM GdA or RAD as they were also the highest doses possible before cell shape changed influencing the CFU assay")`

```{r }
GdA.RAD.dose <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/GdA RAD dose.txt")
dodge <- position_dodge(width=0.6)
ggplot(GdA.RAD.dose, aes(y=Rate, x=Conc, fill=Inhibitor)) +
  geom_bar(stat='identity', position=dodge, width=0.6) +
  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.25) +
  #ggtitle('Hsp90 inhibitor dose response') +
  pdf_theme() +
  theme(legend.position='top') +
  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2)]) +
  ylab("LoH rate/cell division") +
  xlab("Inhibitor concentration (µM)")
```



#Temperature and Hsp90 inhibition synergistically increase LoH

`r margin_note("- plotted are LoH rates with 95\\% confidence intervals")`
`r margin_note("- Strain used MYO1/MYO1::URA3, marking chromosome 5L ")`

```{r}
Comparison <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/Comparison2.txt")
dodge <- position_dodge(width=0.6)
Comparison$Treatment <- relevel(Comparison$Treatment, ref = 'None')
ggplot(Comparison, aes(y=Rate, x=Temperature, fill=Temperature)) +
  geom_bar(stat='identity', position=dodge, width=0.6) +
  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.25) +
  #ggtitle('LoH rates at the MYO1 (Chr 5L) locus in different conditions') +
  facet_grid(. ~ Treatment) +
  pdf_theme() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(legend.position='bottom') +
  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2,4)]) +
  ylab("LoH rate/cell division") +
  xlab("Condition")
```



#Genome-wide LoH rates are affected by temperature and pharmacological inhibition of Hsp90

##Genome-wide LoH rates at 30C and 37C

`r margin_note("- plotted are LoH rates with 95\\% confidence intervals")`
`r margin_note("- p-value = 8.227e-05")`

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Genome <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/LoH genome.txt")
Genome$Locus <- factor(Genome$Locus, levels=c("GAL1", "PHO85", "HCM1", "AXL2",  "TUB4",  "MYO1", "BUD7",  "SAP5",  "LIP4"))
dodge <- position_dodge(width=0.75)
ggplot(subset(Genome, Treatment == '30C' | Treatment == '37C'), aes(y=Rate, x=Locus, fill=Treatment)) +
  geom_bar(stat='identity', position=dodge, width=0.75)+
  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.375) +
  #ggtitle('Genome-wide LoH rates at 37C') +
  pdf_theme() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(legend.position='top') +
  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2)]) +
  ylab("LoH rate/cell division") +
  xlab("Genomic locus")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
WSR <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/WSR_30C_37C.txt")
wilcox.test(WSR$X30C, WSR$X37C)
```


##Genome-wide LoH rates at 30C and 39C

`r margin_note("- plotted are LoH rates with 95\\% confidence intervals")`
`r margin_note("- p-value = 8.227e-05")`

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Genome <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/LoH genome.txt")
Genome$Locus <- factor(Genome$Locus, levels=c("GAL1", "PHO85", "HCM1", "AXL2",  "TUB4",  "MYO1", "BUD7",  "SAP5",  "LIP4"))
dodge <- position_dodge(width=0.75)
ggplot(subset(Genome, Treatment == '30C' | Treatment == '39C'), aes(y=Rate, x=Locus, fill=Treatment)) +
  geom_bar(stat='identity', position=dodge, width=0.75)+
  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.375) +
  #ggtitle('Genome-wide LoH rates at 39C') +
  pdf_theme() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(legend.position='top') +
  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2)]) +
  ylab("LoH rate/cell division") +
  xlab("Genomic locus")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
WSR <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/WSR_30C_39C.txt")
wilcox.test(WSR$X30C, WSR$X39C)
```


##Comparison of genome-wide LoH rates at 37C and 39C

`r margin_note("- plotted are LoH rates with 95\\% confidence intervals")`
`r margin_note("- p-value = 0.3865")`

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Genome <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/LoH genome.txt")
Genome$Locus <- factor(Genome$Locus, levels=c("GAL1", "PHO85", "HCM1", "AXL2",  "TUB4",  "MYO1", "BUD7",  "SAP5",  "LIP4"))
dodge <- position_dodge(width=0.75)
ggplot(subset(Genome, Treatment == '37C' | Treatment == '39C'), aes(y=Rate, x=Locus, fill=Treatment)) +
  geom_bar(stat='identity', position=dodge, width=0.75)+
  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.375) +
  #ggtitle('Genome-wide LoH rates at 37C and 39C') +
  pdf_theme() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(legend.position='top') +
  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2)]) +
  ylab("LoH rate/cell division") +
  xlab("Genomic locus")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
WSR <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/WSR_37C_39C.txt")
wilcox.test(WSR$X37C, WSR$X39C)
```


##Comparison of genome-wide LoH rates at 30C, 37C and 39C

`r margin_note("- plotted are LoH rates with 95\\% confidence intervals")`

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Genome <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/LoH genome.txt")
Genome$Locus <- factor(Genome$Locus, levels=c("GAL1", "PHO85", "HCM1", "AXL2",  "TUB4",  "MYO1", "BUD7",  "SAP5",  "LIP4"))
dodge <- position_dodge(width=0.75)
ggplot(subset(Genome, Treatment == '30C' | Treatment == '37C' | Treatment == '39C'), aes(y=Rate, x=Locus, fill=Treatment)) +
  geom_bar(stat='identity', position=dodge, width=0.75)+
  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.375) +
  #ggtitle('Genome-wide LoH rates at 30C, 37C and 39C') +
  pdf_theme() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(legend.position='top') +
  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2,4)]) +
  ylab("LoH rate/cell division") +
  xlab("Genomic locus")
```

##Genome-wide LoH rates when treated with 3 µM Geldanamycin at 30C

`r margin_note("- plotted are LoH rates with 95\\% confidence intervals")`
`r margin_note("- p-value = 0.0104")`

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Genome <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/LoH genome.txt")
Genome$Locus <- factor(Genome$Locus, levels=c("GAL1", "PHO85", "HCM1", "AXL2",  "TUB4",  "MYO1", "BUD7",  "SAP5",  "LIP4"))
dodge <- position_dodge(width=0.75)
ggplot(subset(Genome, Treatment == '30C' | Treatment == 'Geldanamycin'), aes(y=Rate, x=Locus, fill=Treatment)) +
  geom_bar(stat='identity', position=dodge, width=0.75)+
  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.375) +
  #ggtitle('Genome-wide LoH rates when treated with 3 µM Geldanamycin') +
  pdf_theme() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(legend.position='top') +
  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2)]) +
  ylab("LoH rate/cell division") +
  xlab("Genomic locus")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
WSR <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/WSR_30C_GdA.txt")
wilcox.test(WSR$X30C, WSR$Geldanamycin)
```


##Genome-wide LoH rates when treated with 3 µM Radicicol at 30C

`r margin_note("- plotted are LoH rates with 95\\% confidence intervals")`
`r margin_note("- p-value = 0.017")`

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Genome <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/LoH genome.txt")
Genome$Locus <- factor(Genome$Locus, levels=c("GAL1", "PHO85", "HCM1", "AXL2",  "TUB4",  "MYO1", "BUD7",  "SAP5",  "LIP4"))
dodge <- position_dodge(width=0.75)
ggplot(subset(Genome, Treatment == '30C' | Treatment == 'Radicicol'), aes(y=Rate, x=Locus, fill=Treatment)) +
  geom_bar(stat='identity', position=dodge, width=0.75)+
  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.375) +
  #ggtitle('Genome-wide LoH rates when treated with 3 µM Radicicol') +
  pdf_theme() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(legend.position='top') +
  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2)]) +
  ylab("LoH rate/cell division") +
  xlab("Genomic locus")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
WSR <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/WSR_30C_RAD.txt")
wilcox.test(WSR$X30C, WSR$RAD)
```


##Comparison of genome-wide LoH rates when treated with 3 µM Geldanamycin or Radicicol at 30C

`r margin_note("- plotted are LoH rates with 95\\% confidence intervals")`
`r margin_note("- p-value = 0.9296")`

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Genome <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/LoH genome.txt")
Genome$Locus <- factor(Genome$Locus, levels=c("GAL1", "PHO85", "HCM1", "AXL2",  "TUB4",  "MYO1", "BUD7",  "SAP5",  "LIP4"))
dodge <- position_dodge(width=0.75)
ggplot(subset(Genome, Treatment == '30C' | Treatment == 'Radicicol' | Treatment == 'Geldanamycin'), aes(y=Rate, x=Locus, fill=Treatment)) +
  geom_bar(stat='identity', position=dodge, width=0.75)+
  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.375) +
  #ggtitle('Genome-wide LoH rates when treated with 3 µM Radicicol or Geldanamycin at 30C') +
  pdf_theme() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(legend.position='top') +
  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2,4)]) +
  ylab("LoH rate/cell division") +
  xlab("Genomic locus")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
WSR <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/WSR_GdA_RAD.txt")
wilcox.test(WSR$GdA, WSR$RAD)
```


##Genome-wide LoH rates in the HSP90/hsp90 heterozygous strain at 30C

`r margin_note("- plotted are LoH rates with 95\\% confidence intervals")`
`r margin_note("- p-value = 0.791")`

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Genome <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/LoH genome.txt")
Genome$Locus <- factor(Genome$Locus, levels=c("GAL1", "PHO85", "HCM1", "AXL2",  "TUB4",  "MYO1", "BUD7",  "SAP5",  "LIP4"))
dodge <- position_dodge(width=0.75)
ggplot(subset(Genome, Treatment == '30C' | Treatment == 'HSP90/hsp90'), aes(y=Rate, x=Locus, fill=Treatment)) +
  geom_bar(stat='identity', position=dodge, width=0.75)+
  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.375) +
  #ggtitle('Genome-wide LoH rates in the HSP90/hsp90 heterozygous strain') +
  pdf_theme() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(legend.position='top') +
  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2)]) +
  ylab("LoH rate/cell division") +
  xlab("Genomic locus")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
WSR <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/WSR_30C_HSP90.txt")
wilcox.test(WSR$X30C, WSR$HSP90.hsp90)
```

`r margin_note("- plotted are LoH rates with 95\\% confidence intervals")`

```{r, echo=FALSE, message=FALSE, warning=FALSE}
LoHevents <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/SNP_RFLP.txt")
ggplot(LoHevents, aes(y=Percent, x=Treatment, fill=LoH.event)) +
  geom_bar(stat='identity', width=0.6) +
  facet_grid(~ Locus) +
  #geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.25) +
  #ggtitle('LoH type and rate across the genome') +
  theme(legend.text=element_text(size=20), legend.title=element_text(size=22)) +
  theme(axis.text.x = element_text(size=20,angle=0,hjust=.5,vjust=.5,face="plain"),
        axis.text.y = element_text(size=20,angle=0,hjust=1,vjust=0,face="plain"),
        axis.title.x = element_text(margin=margin(20,0,0,0), size=22,angle=0,hjust=.5,vjust=0,face="bold"),
        axis.title.y = element_text(margin=margin(0,10,0,0), size=22,angle=90,hjust=.5,vjust=.5,face="bold")) +
theme(legend.position='bottom', legend.key=element_rect(size=1, color="white"), legend.key.size=unit(1, "lines")) +
  scale_fill_manual(values=brewer.pal(12, "Set3")[c(1,11,3,5,8,10)]) +
  guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
  ylab("Percent (%)") +
  xlab("Condition") +
  labs(fill="")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
steph <- read.delim("~/Desktop/steph.txt")
expanded<-untable(steph[,-4], num=steph$Count)
expanded$Event<-relevel(expanded$Event, ref='geneConversion')
test <- multinom(Event ~ Chromosome * Treatment, data = expanded)
test2 <- multinom(Event ~ Chromosome + Treatment, data = expanded)
test3 <- multinom(Event ~ Treatment, data = expanded)
coeff <-summary(test)$coefficients
z <- coeff/summary(test)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1))*2
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  anova(test, test2)
)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  anova(test2, test3)
)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  coeff[,1:5]
)
knitr::kable(
  coeff[,6:8]
)

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  p[,1:5]
)
knitr::kable(
  p[,6:8]
)

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
HCM1_MIC<-read.table(file="~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/HCM1_MIC.txt",sep="\t",header=T)
HCM1_MIC<-HCM1_MIC[1:20,1:6]
HCM1_MIC<-gather(HCM1_MIC, "Hsp90_Stress", "MIC")
AOV<-aov(MIC ~ Hsp90_Stress, data=HCM1_MIC)
summary(AOV)
TukeyHSD(AOV)
ggplot(HCM1_MIC, aes(x=Hsp90_Stress, y=MIC, colour=Hsp90_Stress))+
  geom_jitter(size=3, position = position_jitter(width = .3))+
  ylab("MIC")+
  xlab("")+
  sd_theme()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=12),
        axis.text.y = element_text(size=12),
        axis.title.y=element_text(size=14, face='bold'),
        legend.position="none"
        ) +
  scale_color_manual(values=c(rep("dodgerblue2", 3),rep("lightseagreen",3)))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Genome <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/DataFiles/LoH genome.txt")
#Genome$Locus <- factor(Genome$Locus, levels=c("GAL1", "PHO85", "HCM1", "AXL2",  "TUB4",  "MYO1", "BUD7",  "SAP5",  "LIP4"))
#dodge <- position_dodge(width=0.75)
#ggplot(subset(Genome, Treatment == '30C' | Treatment == '39C'), aes(y=Rate, x=Locus, fill=Treatment)) +
#  geom_bar(stat='identity', position=dodge, width=0.75)+
#  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.375) +
#  #ggtitle('Genome-wide LoH rates at 39C') +
#  sd_theme() +
#  theme(legend.text=element_text(size=20), legend.title=element_text(size=22)) +
#  theme(axis.text.x = element_text(size=20,angle=45,hjust=1,vjust=1,face="italic"),
#        axis.text.y = element_text(size=20,angle=0,hjust=1,vjust=0,face="plain"),  
#        axis.title.x = element_text(margin=margin(30,0,0,0), size=22,angle=0,hjust=.5,vjust=0,face="bold"),
#        axis.title.y = element_text(margin=margin(0,30,0,0), #size=22,angle=90,hjust=.5,vjust=.5,face="bold")) +
#  theme(legend.position='top') +
#  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2)]) +
#  ylab("LoH rate/cell division") +
#  xlab("Genomic locus")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#WSR <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/WSR.txt")
#wilcox.test(WSR$X30C, WSR$Geldanamycin)
```

```{r}
#mylog_trans <- function(base=exp(1), from=0) 
#{
#  trans <- function(x) log(x, base)-from
#  inv <- function(x) base^(x+from)
#  trans_new("mylog", trans, inv, log_breaks(n=0-from, base=base), 
#            domain = c(base^from, Inf))
#}
#Fluconazole <- read.delim("~/Dropbox/! Diezmann Lab/R/LoH/Fluconazole dose.txt")
#ggplot(Fluconazole, aes(y=Rate, x=Fluconazole, fill=factor(Conc))) +
#dodge <- position_dodge(width=0.3)
#  geom_bar(stat='identity', position=dodge, width=0.3) +
#  geom_errorbar(aes(ymax=Rate+CI, ymin=Rate-CI), position=dodge, width=0.125) +
#  scale_y_continuous(trans=mylog_trans(base=10, from=-7)) +#(limits=c(0,0.00025)) +
#  ggtitle('Fluconazole dose response') +
#  sd_theme() +
#  theme(legend.position='top') +
#  scale_fill_manual(values=brewer.pal(12, "Paired")[c(1,2)], name='GdA (µM)') +
#  ylab("LoH rate/cell division") +
#  xlab("Fluconazole concentration (µg/ml)")
##no error bars because CIs are less than zero
```

